---
output:
  html_document:
    df_print: paged
params:
  fp_df: !r NULL
  p_df: !r NULL
title: "Analysis Template"

---

```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(cowplot)
library(kableExtra)
library(ggthemes)
library(magrittr)
library(dplyr)
library(tidyr)

drake::loadd(fp_single_drk)
drake::loadd(jnd_res_drk)
drake::loadd(fp_group_drk)

fp_df = params$fp_df
fp_df = fp_single_drk
p_df = jnd_res_drk
fp_group = fp_group_drk
```

# Checking the results

### P-value distributions across iterations by dataset
Check distribution is uniform. Dips in the limits are normal.

```{r}
long_p_df = p_df %>% pivot_longer(cols=starts_with('rt_'), names_to = "pp", values_to = "p")

ggplot(long_p_df, aes(x=p, color=dataset)) +
  geom_density() +
  theme_tufte(base_family = 'sans') +
  labs(title='p-value distribution across PPs and iterations by dataset',
       x = 'p-value')

```


### False positive when considering a single preprocessing pipeline
All values should be tightly concentrated along the .05 line. Otherwise the expected false positive rate defined by the alpha-level is not achieved.
```{r}
long_fp_df = fp_df %>% pivot_longer(cols=matches('^[a-z]{3}_'), names_to = "pp", values_to = "fp")

ggplot(long_fp_df, aes(x=fp)) +
  geom_density() +
  theme_tufte(base_family = 'sans') +
  geom_vline(xintercept = .05, linetype=2)+
  labs(title='FP in single pipelines',
       x = "False Positive rate (alpha = .05)")
```

# Figures for the paper

## Table

```{r}
fp_group %>% kable() %>% kable_styling()
```


## Figure
```{r}

```

